\documentclass[11pt,a4paper]{letter}

\usepackage[hidelinks]{hyperref}
\usepackage{geometry}
\geometry{margin=1in}

\begin{document}

\begin{letter}{Hiring Manager \\ Roku \\ Manchester, UK}

\opening{Dear Hiring Manager,}

I am writing to express my interest in the Software Engineer Intern (Java) position at Roku in Manchester. As a Physics graduate with strong foundations in programming, analytical problem solving, and system design, I am particularly drawn to this role because of its focus on scalable backend systems and experimentation platforms.

Throughout my degree, I have developed structured and modular software across multiple technical projects. In my quantum computing project, I built cloud-based programs that interacted with distributed systems, applying object-oriented design principles to ensure maintainability and clarity. I also performed statistical analysis on experimental outputs using hypothesis testing and data modelling techniques, which align closely with experimentation frameworks and A/B testing concepts.

My background in physics has strengthened my ability to reason about complex systems, optimise performance, and approach problems methodically. In addition, my experience working as a computer technician required systematic debugging, reliability testing, and clear communication within a team environment.

I am particularly interested in Roku’s work on large-scale experimentation and backend infrastructure. The opportunity to contribute to production-level systems while learning from experienced engineers would be an ideal next step in my development as a software engineer.

Thank you for your time and consideration. I would welcome the opportunity to further discuss how my skills and enthusiasm align with your team.

\closing{Kind regards,}

Zaher Faruk \\
07553 064043 \\
\href{mailto:zaherfaruk04@gmail.com}{zaherfaruk04@gmail.com} \\
\href{https://www.linkedin.com/in/zaher-faruk/}{linkedin.com/in/zaher-faruk}

\end{letter}

\end{document}
