%-------------------------
% Resume in Latex
% Author : Zaher Faruk
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Zaher Faruk} \\ \vspace{1pt}
    \small 07553064043 $|$ \href{mailto:zaherfaruk04@gmail.com}{\underline{zaherfaruk04@gmail.com}} $|$
    \href{https://www.linkedin.com/in/zaher-faruk/}{\underline{linkedin.com/in/zaher-faruk/}} $|$
    \href{https://github.com/ZaherFaruk04}{\underline{github.com/ZaherFaruk04}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Salford}{Salford, England}
      {BSc (Hons) Physics}{September 2022 to July 2025}
    \resumeSubheading
      {Ashton Sixth Form College}{Ashton under Lyne, England}
      {A Levels in Maths, Physics and Computer Science}{September 2020 to July 2022}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Office Administrator}{Ashton under Lyne, England}
      {Leap Family Contact Centre}{September 2025 to Present}
      \resumeItemListStart
        \resumeItem{Supported operational processes and ensured compliance with internal procedures, contributing to safe working practices and consistent service delivery.}
        \resumeItem{Managed documentation, scheduling and reporting systems that aligned with organisational standards and supported contract performance.}
        \resumeItem{Engaged with staff and clients to resolve enquiries, supporting positive customer experience and reinforcing strong working relationships.}
        \resumeItem{Identified opportunities for workflow improvement and supported implementation of more efficient administrative processes.}
      \resumeItemListEnd

    \resumeSubheading
      {Computer Technician}{Ashton under Lyne, England}
      {Microtech Computers}{September 2018 to August 2019}
      \resumeItemListStart
        \resumeItem{Installed and configured operating systems with a focus on safe working procedures, quality checks and compliance with technical requirements.}
        \resumeItem{Conducted system testing to verify stability and reduce operational risk, ensuring repairs met required standards.}
        \resumeItem{Supported customers with technical issues, maintaining strong communication and service quality.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Producing and Engineering a Drone} $|$ \emph{C++, Fusion 360, Arduino}}{September 2023 to June 2024}
      \resumeItemListStart
        \resumeItem{Designed and assembled hardware components with attention to safe operation, system reliability and compliance with technical constraints.}
        \resumeItem{Developed control algorithms and tested system performance, identifying issues and implementing improvements.}
        \resumeItem{Created CAD models to support accurate manufacturing and operational efficiency.}
        \resumeItem{Troubleshot hardware and software faults, improving system stability and performance.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Programming Quantum Computers} $|$ \emph{IBM Quantum, PennyLane, Azure}}{October 2024 to Present}
      \resumeItemListStart
        \resumeItem{Worked with advanced technical systems, demonstrating strong analytical capability and adaptability to new operational models.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Non Analytic Basins and Chaotic System Simulation} $|$ \emph{MATLAB}}{September 2024 to October 2024}
      \resumeItemListStart
        \resumeItem{Modelled complex systems using numerical methods, strengthening analytical and data interpretation skills relevant to monitoring and reporting.}
        \resumeItem{Produced visual outputs to communicate system behaviour clearly and accurately.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Lennard Jones Potential Plotting} $|$ \emph{Python, NumPy, Matplotlib}}{October 2023 to November 2024}
      \resumeItemListStart
        \resumeItem{Processed and analysed data sets to model physical interactions, supporting evidence based decision making.}
        \resumeItem{Created visualisations to communicate findings clearly and support operational understanding.}
        \resumeItem{Optimised algorithms to improve efficiency and accuracy.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------HOBBIES-----------
\section{Hobbies}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kyokushin Karate}{Springhead, England}
      {Oldham Kyokushinkai Karate}{March 2024 to Present}
      \resumeItemListStart
        \resumeItem{Developed discipline, resilience and focus through rigorous physical training.}
        \resumeItem{Gained appreciation for cultural and philosophical aspects of martial arts.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}
