\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Zaher Faruk} \\ \vspace{1pt}
    \small 07553064043 $|$ \href{mailto:zaherfaruk04@gmail.com}{\underline{zaherfaruk04@gmail.com}} $|$
    \href{https://www.linkedin.com/in/zaher-faruk/}{\underline{linkedin.com/in/zaher-faruk/}} $|$
    \href{https://github.com/ZaherFaruk04}{\underline{github.com/ZaherFaruk04}}
\end{center}

\section{Profile}
\small{
Physics graduate with strong analytical and programming skills, seeking a Software Engineer Intern role within engineering-focused development teams. Experienced in object-oriented programming, simulation, numerical modelling and data visualisation using C++, Python, MATLAB and Java. Motivated to contribute to high-quality engineering software in an agile environment.
}

\section{Technical Skills}
\small{
\textbf{Programming:} Python, C++, Java (academic), MATLAB, Arduino \\
\textbf{Software Engineering:} Object Oriented Design, debugging, testing, version control (Git) \\
\textbf{Engineering \& Data:} Simulation, numerical methods, data analysis, visualisation \\
\textbf{Tools:} NumPy, Pandas, Matplotlib, Fusion 360, Tinkercad, Excel \\
\textbf{Systems:} Windows, Linux/UNIX \\
\textbf{Core Competencies:} Problem solving, teamwork, communication, attention to detail
}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {The University of Salford}{Salford, England}
    {BSc (Hons) Physics, 2:1}{September 2022 to July 2025}
  \resumeSubheading
    {Ashton Sixth Form College}{Ashton under Lyne, England}
    {A Levels in Maths, Physics and Computer Science}{September 2020 to July 2022}
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Producing and Engineering a Drone} $|$ \emph{C++, Arduino, Fusion 360, Tinkercad}}{Sep 2023 -- Jun 2024}
    \resumeItemListStart
      \resumeItem{Developed and programmed a real-time flight control system using C++ on Arduino.}
      \resumeItem{Designed and assembled electronic components including motors, ESCs and flight controller.}
      \resumeItem{Created custom mechanical components using CAD modelling in Fusion 360.}
      \resumeItem{Diagnosed and resolved hardware faults and software bugs during testing and integration.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Programming Quantum Computers} $|$ \emph{IBM Quantum, PennyLane, Azure Quantum}}{Oct 2024 -- Present}
    \resumeItemListStart
      \resumeItem{Developed programs to run and compare algorithms across multiple quantum computing platforms.}
      \resumeItem{Worked with diverse architectures including superconducting qubits, photonic systems, trapped ions and quantum annealers.}
      \resumeItem{Analysed system behaviour, constraints and performance differences between platforms.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Non-Analytic Basins and Chaotic System Simulation} $|$ \emph{MATLAB}}{Sep 2024 -- Oct 2024}
    \resumeItemListStart
      \resumeItem{Numerically solved nonlinear ODEs using MATLAB’s \texttt{ode45} solver.}
      \resumeItem{Analysed sensitivity to initial conditions through perturbed simulations.}
      \resumeItem{Generated time-series and 3D phase-space visualisations of chaotic attractors.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Lennard-Jones Potential Modelling} $|$ \emph{Python, NumPy, Pandas, Matplotlib}}{Oct 2023 -- Nov 2024}
    \resumeItemListStart
      \resumeItem{Processed experimental data from CSV files using Pandas.}
      \resumeItem{Implemented mathematical models of interatomic forces using NumPy.}
      \resumeItem{Produced high-resolution plots comparing theoretical and experimental results.}
      \resumeItem{Optimised algorithms to generate smooth and accurate visualisations.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Office Administrator}{Ashton under Lyne, England}
    {Leap Family Contact Centre}{September 2025 to Present}
    \resumeItemListStart
      \resumeItem{Maintained accurate digital records and supported internal systems.}
      \resumeItem{Coordinated workflows and ensured data consistency across teams.}
    \resumeItemListEnd

  \resumeSubheading
    {Computer Technician}{Ashton under Lyne, England}
    {Microtech Computers}{September 2018 to August 2019}
    \resumeItemListStart
      \resumeItem{Installed and configured Windows and Linux operating systems.}
      \resumeItem{Diagnosed and resolved hardware and software faults.}
      \resumeItem{Performed testing to ensure system reliability and quality.}
    \resumeItemListEnd

\resumeSubHeadingListEnd



\end{document}
