%-------------------------------------------------
% Spotify 2026 Summer Internship
% CV (Page 1) + Cover Letter (Page 2)
%-------------------------------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\large\raggedright
}{}{0em}{}[\titlerule \vspace{-6pt}]

\begin{document}

%==========================
% PAGE 1 — CV
%==========================

\begin{center}
  {\Huge \scshape Zaher Faruk} \\ \vspace{4pt}
  \small
  07553 064043 \,|\, 
  \href{mailto:zaherfaruk04@gmail.com}{zaherfaruk04@gmail.com} \,|\, 
  \href{https://www.linkedin.com/in/zaher-faruk/}{linkedin.com/in/zaher-faruk} \,|\, 
  \href{https://github.com/ZaherFaruk04}{github.com/ZaherFaruk04}
\end{center}

\vspace{-6pt}

\section{Profile}
\small{
Physics graduate with strong experience in data analysis, computational modelling, and software-based problem solving. Proficient in Python, C++, and MATLAB, with hands-on experience analysing complex systems, building visualisations, and improving system performance through iterative testing. Motivated to apply data science and engineering techniques to large-scale, data-driven products, particularly those focused on user experience, personalisation, and platform reliability.
}

\section{Technical Skills}
\small{
\textbf{Programming Languages:} Python, C++, MATLAB \\
\textbf{Data Science \& Analytics:} Exploratory data analysis, regression, numerical modelling, anomaly detection, hypothesis testing \\
\textbf{Libraries \& Tools:} Pandas, NumPy, Matplotlib, Excel, Fusion 360 \\
\textbf{Engineering Concepts:} Algorithms, debugging, system reliability, performance analysis, modelling system behaviour \\
\textbf{Ways of Working:} Data-driven decision making, cross-functional collaboration, structured problem solving
}

\section{Education}
\small{
\textbf{University of Salford} \hfill Salford, UK \\
BSc (Hons) Physics 
}

\section{Experience}
\small{
\textbf{Office Administrator} — Leap Family Contact Centre \hfill Sep 2025 -- Present \\
Maintained structured datasets, documentation, and recurring reports to support operational and management decision making. Collaborated with cross-functional teams, ensured data accuracy, and supported process improvements through reliable reporting and communication.

\vspace{4pt}

\textbf{Computer Technician} — Microtech Computers \hfill Sep 2018 -- Aug 2019 \\
Diagnosed and resolved hardware and software issues, installed and configured operating systems, and tested system performance. Developed strong debugging, analytical, and problem-solving skills in a technical environment.
}

\section{Projects}
\small{

\textbf{Producing and Engineering a Drone} — C++, Arduino, Fusion 360 \hfill Sep 2023 -- Jun 2024 \\
Designed and assembled hardware components with a focus on system reliability, safety, and operational constraints. Developed and tested control algorithms, analysed performance data to identify faults, and implemented iterative improvements. Created CAD models to support accurate manufacturing and efficient system integration. Troubleshot hardware and software issues to improve system stability and performance, applying structured engineering and debugging practices.

\vspace{6pt}

\textbf{Programming Quantum Computers} — IBM Quantum, PennyLane, Azure \hfill Oct 2024 -- Present \\
Worked with cloud-based quantum computing platforms, adapting to new computational models and APIs. Designed and executed experiments, analysed outputs, and interpreted results to understand system behaviour and performance. Demonstrated strong analytical capability, rapid learning, and adaptability when working with complex and unfamiliar technical systems.

\vspace{6pt}

\textbf{Non-Analytic Basins and Chaotic System Simulation} — MATLAB \hfill Sep 2024 -- Oct 2024 \\
Modelled complex nonlinear systems using numerical methods, generating datasets that captured system evolution and sensitivity to initial conditions. Produced visual outputs to communicate system behaviour clearly, strengthening skills in data interpretation, monitoring, and analytical reporting.

\vspace{6pt}

\textbf{Lennard-Jones Potential Plotting and Analysis} — Python, NumPy, Matplotlib \hfill Oct 2023 -- Nov 2024 \\
Processed and analysed datasets to model physical interactions, supporting evidence-based conclusions through computational analysis. Built visualisations to communicate findings clearly and support operational understanding. Optimised algorithms to improve computational efficiency and accuracy, reinforcing performance-aware programming practices.
}

\section{Interests}
\small{
Music technology, data-driven product development, large-scale data systems, user experience optimisation, martial arts
}

%==========================
% PAGE BREAK
%==========================
\newpage

%==========================
% PAGE 2 — COVER LETTER
%==========================

\begin{flushleft}
\textbf{Zaher Faruk} \\
Ashton-under-Lyne, UK \\
07553 064043 \\
zaherfaruk04@gmail.com \\
linkedin.com/in/zaher-faruk
\end{flushleft}

\vspace{1cm}

\begin{flushleft}
\textbf{Hiring Team} \\
Spotify \\
London, UK
\end{flushleft}

\vspace{0.5cm}

\textbf{Re: 2026 Summer Internship — Engineering \& Data Science (London)}

\vspace{0.5cm}

Dear Hiring Team,

\vspace{0.3cm}

I am writing to apply for the 2026 Summer Internship in Engineering and Data Science at Spotify. I am highly motivated to contribute to a company where engineering and data play a central role in shaping user experience at global scale.

Throughout my degree, I have developed strong skills in Python, C++, and MATLAB through projects involving data analysis, numerical modelling, and system simulation. I have regularly worked with large datasets, built visualisations to communicate insights, and analysed system behaviour to identify performance issues and improvement opportunities. These experiences align closely with Spotify’s data-driven approach to understanding listeners, content, and product performance.

In addition to my academic work, I have gained hands-on experience in technical and operational environments. As a Computer Technician, I diagnosed and resolved system faults using structured debugging approaches. In my current administrative role, I work with structured data, reporting, and cross-functional teams, ensuring accuracy and supporting operational decision making. Together, these roles have strengthened both my technical problem-solving ability and my communication skills.

I am particularly drawn to Spotify’s culture of learning, collaboration, and continuous improvement. I would be excited to contribute as either a Data Science Intern or Engineering Intern, with a strong preference for data-focused roles where insights directly influence product decisions and user experience.

Thank you for considering my application. I would welcome the opportunity to bring my curiosity, analytical mindset, and technical skills to Spotify’s London internship cohort.

\vspace{0.5cm}

Yours sincerely, \\[4pt]
\textbf{Zaher Faruk}

\end{document}
